Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-23 paper/paper.tex
pass on 3

Finally, \tname{} ranks plausible rules according to heuristics
learned from a database of existing rules. The intuition is that new
rules should share characteristics with pre-existing rules. For
example, one heuristic function used by \tname{} leverages the amount
of options a rule typically has. The score of a rule, given by this
function, is proportional to the popularity of the number of options
declared in rules of a given
protocol. Figure~\ref{fig:distribution-contents} shows the
distribution of the number of content options for the database of
rules we used\Mar{reference}. Note that rules with 1 to 3 options are
more common.  At the end of the process, \tname{} ranks the golden
rule at the top of the ranking including \Fix{XXXXXX} other plausible
rules.

>>>>

Finally, \tname{} ranks plausible rules according to heuristics
learned from a database of existing rules. The intuition is that new
rules should share characteristics with pre-existing rules. For
example, one heuristic function used by \tname{} leverages the amount
of options a rule typically has. The score of a rule, given by this
function, is proportional to the popularity of the number of options
declared in rules of a given
protocol. Figure~\ref{fig:distribution-contents} shows the
distribution of the number of content options for the database of
rules we used\Mar{reference} \Luc{essa distribuicao n eh utilizada 
para pontuar as regras desse exemplo, n seria mais interessante citar outra?
poderia ser a de tamanhos das regras.}. Note that rules with 1 to 3 options 
are more common \Luc{1 to 3 \textbf{content} options}. At the end of the 
process, \tname{} ranks the golden rule at the top of the ranking 
including \Fix{XXXXXX} other plausible rules.
